---
title: "General mixed linear models"
author: "Tracy Sánchez"
date: "Última actualización: `r format(Sys.Date(), format = '%d %B %Y')`" 
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
    toc_depth: 6
    mathjax: null
    css: doc.css # To set style to maximum in a separate file
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA) # To delete all hashtags from output in HTML 
library(readr);library(dlookr);library(dplyr);
library(lme4);library(car);library(emmeans);library(MASS);library(jtools);
library(lmerTest);library(gmodels);library(nlme); library(multcompView);
library(ggplot2)
library(sjPlot)
library(sjstats)
emm_options(lmerTest.limit = 10000)
emm_options(pbkrtest.limit = 10000)
```

# Loading Data 

```{r echo = FALSE,warning = FALSE }
HumanA <- read.csv("/Volumes/TwoTeras/2_DataSets_Experiments_1_2/humanA_Behavioural.csv", sep =",")
head(HumanA)
```
Here we eliminate the cases that do not have a complete set of eyet-racking data.
Last two subjects come from experiment 2. 

```{r }
#HumanA <- HumanA %>% dplyr::filter(!ID %in% c(0479, 2361, 3246, 3572, 3976, 5238, 5531, 5895, 7264, 4580, 3540))
```

# Recoding for effects and formating factors 
```{r }

HumanA$ContextEffectf <-dplyr::recode(HumanA$Context, 
                                      False = -0.5, True= 0.5,
                                      .default = NaN)
HumanA$AgentPresence <-dplyr::recode(HumanA$AvatarPresenceCategory,
                                             Omitted = -0.5, Present= 0.5,
                                             .default = NaN)
HumanA$ContextEffectf <-factor(HumanA$ContextEffectf,levels= c(-0.5, 0.5), 
                               labels=c('Residential', 'Public')) 
HumanA$AgentPresencef <-factor(HumanA$AgentPresence,
                                levels= c(-0.5, 0.5), 
                                labels=c('Omitted', 'Displayed')) 
```
# Data descriptives
```{r}
MainVariables <- subset(HumanA, select = c(AbsolutError, RT, Alter))
describe(MainVariables)
```
```{r}
summary(HumanA$AgentPresence)

```


```{r}
df = HumanA[complete.cases(HumanA),]

ggplot(df,aes(x=AbsolutError,group=AgentPresence,fill=AgentPresence))+
  geom_histogram(position="identity",alpha=0.5,binwidth=10)+  facet_grid(cols = vars(ContextEffectf))+theme_bw()
```

```{r }
library(dplyr)
TwoFactorTable <- HumanA %>% 
  group_by(ContextEffectf, AgentPresencef)%>%
  summarise(AccuracyMean = mean(AbsolutError, na.rm = TRUE),
            n=n(),
            AccuracyStandardDev = sd(AbsolutError, na.rm = TRUE),
            RTMean = mean(RT, na.rm = TRUE),
            RTStandardDev = sd(RT, na.rm = TRUE))
library(tidyr)
TwoFactorTableUnite <- TwoFactorTable %>%
  unite("TwoFactor", ContextEffectf:AgentPresencef, sep= " ", remove = F)
  
TwoFactorTableUnite <-  TwoFactorTableUnite %>%
  mutate( AccuracyStandardError=AccuracyStandardDev/sqrt(n)) %>%  
  mutate( AccuracyStandardIC=AccuracyStandardDev * qt((1-0.05)/2 + .5, n-1)) %>%
  mutate( RTStandardError=RTStandardDev/sqrt(n)) 

OneFactorTable <- HumanA %>% 
  group_by(ContextEffectf)%>%
  summarise(AccuracyMean = mean(AbsolutError, na.rm = TRUE),
            n=n(),
            AccuracyStandardDev = sd(AbsolutError, na.rm = TRUE),
            RTMean = mean(RT, na.rm = TRUE),
            RTStandardDev = sd(RT, na.rm = TRUE))
library(tidyr)
  
OneFactorTable <-  OneFactorTable %>%
  mutate( AccuracyStandardError=AccuracyStandardDev/sqrt(n)) %>%  
  mutate( AccuracyStandardIC=AccuracyStandardDev * qt((1-0.05)/2 + .5, n-1)) %>%
  mutate( RTStandardError=RTStandardDev/sqrt(n)) 

```

 

```{r echo=FALSE}
legend_title <- "Agent Presence on the Stimuli"
Acc_two <- ggplot(data = subset(TwoFactorTableUnite, !is.na(AgentPresencef)),
              aes(x = ContextEffectf,
                  y = AccuracyMean,
                  group = AgentPresencef))

Acc_two + geom_point(aes(shape = AgentPresencef, linetype = AgentPresencef), position = position_dodge(0.3)) +
  geom_errorbar(aes(linetype = AgentPresencef, ymin = AccuracyMean - AccuracyStandardError, 
                    ymax = AccuracyMean + AccuracyStandardError),
                position = position_dodge(0.3),
                width = 0.2,
                size = 0.7) +
  theme_bw() +
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold"),
        legend.position="top",
        legend.background = element_rect(fill="gray88",
                                  size=0.5, linetype="solid", 
                                  colour ="gray88"),
        plot.caption = element_text(hjust = 0))  +
  ylab("Average absolute angular error in degrees") +
  xlab("Location") +
  ggtitle("Accuracy performance",
          subtitle = "The effects of location and agent category") +
  labs(caption = paste0("Error bars indicate one Standard Error \n"),
       linetype = legend_title,
       shape = legend_title)

legend_title <- "Agent Presence on the Stimuli"
Acc_One <- ggplot(data = subset(OneFactorTable, !is.na(ContextEffectf)),
              aes(x = ContextEffectf,
                  y = AccuracyMean))

Acc_One + geom_point(aes(shape = ContextEffectf, linetype = ContextEffectf), position = position_dodge(0.3)) +
  geom_errorbar(aes(linetype = ContextEffectf, ymin = AccuracyMean - AccuracyStandardError, 
                    ymax = AccuracyMean + AccuracyStandardError),
                position = position_dodge(0.3),
                width = 0.2,
                size = 0.7) +
  theme_bw() +
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold"))  +
  ylab("Average absolute angular error in degrees") +
  xlab("Location") +
  ggtitle("Accuracy performance",
          subtitle = "The effects of location and agent category") +
  labs(caption = paste0("Error bars indicate one Standard Error \n"))
       
```

```{r echo=FALSE}
# Response Time 
RT_two <- ggplot(data = subset(TwoFactorTableUnite, !is.na(AgentPresencef)),
              aes(x = ContextEffectf,
                  y = RTMean,
                  group = AgentPresencef))

RT_two + geom_point(aes(shape = AgentPresencef, linetype = AgentPresencef), position = position_dodge(0.3)) +
  geom_errorbar(aes(linetype = AgentPresencef, ymin = RTMean - RTStandardError, 
                    ymax = RTMean + RTStandardError),
                position = position_dodge(0.3),
                width = 0.2,
                size = 0.7) +
  theme_bw() +
   theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold"),
        legend.position="top",
        legend.background = element_rect(fill="gray88",
                                  size=0.5, linetype="solid", 
                                  colour ="gray88"),
        plot.caption = element_text(hjust = 0)) +
  ylab("Response Time in seconds") +
  xlab("Location") +
  ggtitle("Response time:",
          subtitle = "The effects of location and agent category") +
  labs(caption = paste0("Error bars indicate one Standard Error \n"),
       linetype = legend_title,
       shape = legend_title)

```



## Checking for the distribution of Absolut error
```{r warning = FALSE }
df = HumanA[complete.cases(HumanA),]
df$AbsolutErrorR <- round(df$AbsolutError, digits = 3)
qqp(df$AbsolutErrorR, "norm")
qqp(df$AbsolutErrorR, "lnorm")
```
```{r warning = FALSE }
n_distinct(df$ID)
# Set up contrast to sum zero A.K.A compare each level equally
contrasts(df$ContextEffectf) <- "contr.sum"
contrasts(df$AgentPresencef) <- "contr.sum"
```

# Linear mixed models

## Assessing the need for a multilevel model

```{r}
interceptOnly <-gls(AbsolutError ~ 1, data = df, 
                    method = "ML")
IDrandomInterceptOnly <-lmer(AbsolutError~ 1 + (1|ID), data = df)
StartlocationsrandomIntercept <-lmer(AbsolutError ~ 1 + (1|ID) + (1|PointingTaskStartingLocations), data = df)
```

```{r}
m1 <- lm(AbsolutError ~ ContextEffectf*AgentPresencef, data=df)
m2 <- lmer(AbsolutError ~ ContextEffectf*AgentPresencef + 1 + (1|ID) + (1|PointingTaskStartingLocations), data=df, REML = F)
anova(m2, m1)
```

## Absolut Error Models

I am adding one main factor at a time 

```{r}
TwofactorInteraction <-update(StartlocationsrandomIntercept, .~.  + ContextEffectf*AgentPresencef)
summary(TwofactorInteraction)
Anova(TwofactorInteraction)
#Pairwise<- emmeans(TwofactorInteraction, pairwise ~ ContextEffectf*AgentPresencef)
#Pairwise
#plot(Pairwise[[2]], CIs = TRUE)
tab_model(TwofactorInteraction, pred.labels=c("Intercept", "Location context (Public vs. Residential)", "Agent presence in task stimuli", "Location x Agent Presence"))
```


```{r}
library(glmmTMB)
library(sjPlot)
plot_model(TwofactorInteraction, type="re")
plot_model(TwofactorInteraction, type="est")
plot_model(TwofactorInteraction, type="pred")
plot_model(TwofactorInteraction, type="int", mdrt.values = "quart")
```

```{r}
plot_model(TwofactorInteraction, show.values = TRUE, value.offset = .3, title = "LMM predictor estimates for absolute angular error", axis.labels = c("Location * Agent presence on the task stimuli","Agent presence on the task stimuli","Location (Public vs. Residential"), colors="bw",  vline.color = "red")
```

```{r}
means_Context_1 <- lsmeans(TwofactorInteraction, ~  ContextEffectf)
means_Presence_1 <- lsmeans(TwofactorInteraction, ~  AgentPresencef) 
```

```{r}
# To convert from lsmeans output 

d <- data.frame(means_Context_1)


ggplot(data = d,aes(x = ContextEffectf, y = lsmean)) +
geom_point(aes(shape = ContextEffectf, linetype = ContextEffectf), position = position_dodge(0.3)) +
geom_errorbar(aes(linetype = ContextEffectf, ymin = lsmean - SE, ymax = lsmean + SE),
                position = position_dodge(0.3),
                width = 0.2,
                size = 0.7) + theme_bw() +
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold"),
        legend.position="top",
        legend.background = element_rect(fill="gray88",
                                  size=0.5, linetype="solid", 
                                  colour ="gray88"),
        plot.caption = element_text(hjust = 0)) +
  ylab("Estimated marginal means for absolute angular error") +
  xlab("Location") +
  ggtitle("Estimated marginal means:",
          subtitle = "The location effect") +
  labs(caption = paste0("Error bars indicate one one standard errors associated with each estimated marginal mean \n"),
       linetype = legend_title,
       shape = legend_title)

d <- data.frame(means_Presence_1)


ggplot(data = d,aes(x = AgentPresencef, y = lsmean)) +
geom_point(aes(shape = AgentPresencef, linetype = AgentPresencef), position = position_dodge(0.3)) +
geom_errorbar(aes(linetype = AgentPresencef, ymin = lsmean - SE, ymax = lsmean + SE),
                position = position_dodge(0.3),
                width = 0.2,
                size = 0.7) +
theme_bw() +
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold"),
        legend.position="top",
        legend.background = element_rect(fill="gray88",
                                  size=0.5, linetype="solid", 
                                  colour ="gray88"),
        plot.caption = element_text(hjust = 0)) +
  ylab("Estimated marginal means for absolute angular error") +
  xlab("Location") +
  ggtitle("Estimated marginal means:",
          subtitle = "The agent stimuli presence effect") +
  labs(caption = paste0("Error bars indicate one one standard errors associated with each estimated marginal mean \n"),
       linetype = legend_title,
       shape = legend_title)
```

```{r}
library(multcomp);library(multcompView)
CLD <- cld(Pairwise,
          alpha=0.05,
          Letters=letters,
          adjust="sidak")
ggplot(CLD,
       aes(x     = ContextEffectf,
           y     = emmean,
           group = AgentPresencef,
           colours = .group)) +

    geom_point(aes(shape=AgentPresencef, linetype =AgentPresencef), position=position_dodge(0.3)) +

    geom_errorbar(aes(linetype=AgentPresencef,
                      ymin  =  lower.CL,
                      ymax  =  upper.CL),
                      position=position_dodge(0.3),
                      width =  0.2,
                      size  =  0.7) +

    theme_bw() +
    theme(axis.title   = element_text(face = "bold"),
          axis.text    = element_text(face = "bold"),
          plot.caption = element_text(hjust = 0)) +

    ylab("Estimated marginal mean\ Absolute angular error") +
    xlab("Location location") +
    ggtitle ("Marginal Means",

             subtitle = "location * Presence") +

                 labs(caption  = paste0( 
                                   "Boxes indicate the EM mean. \n",
                                   "Error bars indicate the 95% ",
                                   "confidence interval of the EM mean. \n"),
                            hjust=0.5) 
```

```{r}
anova(IDrandomInterceptOnly, StartlocationsrandomIntercept, 
      MeaningfulContext, Presence, TwofactorInteraction )
```

```{r}
plot(TwofactorInteraction, which = 1)
plot(MeaningfulContext, which = 1)
```
```{r}
GHQ <- glmer(AbsolutError ~  ContextEffectf*AgentPresencef + (1|ID), data = HumanA,family=gaussian(link = "log"), nAGQ = 25)  
summary(GHQ)
Anova(GHQ)
anova(GHQ)
emmeans(GHQ, pairwise ~ ContextEffectf:AgentPresencef, type = "response")
```
```{r}
plot(fitted(GHQ), residuals(GHQ), xlab = "Fitted Values", ylab = "Residuals")
abline(h = 0, lty = 2)
lines(smooth.spline(fitted(GHQ), residuals(GHQ)))
```
```{r}
interceptOnly <-gls(log(AbsolutError) ~ 1, data = df, 
                    method = "ML")
IDrandomInterceptOnly <-lme(log(AbsolutError) ~ 1, data = df,  
                            random =~1|ID,
                            method = "ML")
StartlocationsrandomIntercept <-update(IDrandomInterceptOnly, .~.,   
                              random=~1|ID/PointingTaskStartingLocations,
                              method= "ML")
MeaningfulContext <-update(StartlocationsrandomIntercept, .~. + ContextEffectf)
Presence <-update(MeaningfulContext, .~. + AgentPresencef)
TwofactorInteraction <-update(Presence, .~. + ContextEffectf*AgentPresencef)
summary(TwofactorInteraction)
Anova(TwofactorInteraction)
Pairwise<- emmeans(TwofactorInteraction, pairwise ~ ContextEffectf*AgentPresencef, type='response')
Pairwise 
plot(Pairwise[[2]])
anova(interceptOnly, IDrandomInterceptOnly, StartlocationsrandomIntercept, 
      MeaningfulContext, Presence, TwofactorInteraction )
plot(TwofactorInteraction, which = 1)
```
```{r}
model <- glmmPQL(RT ~  ContextEffectf*AgentPresencef, ~1|ID/PointingTaskStartingLocations,  family = gaussian(link = "log"), data = HumanA, verbose = FALSE)
summary(model)
```




## Response Time models 
## Checking for the distribution of RT
```{r warning = FALSE }
df = HumanA[complete.cases(HumanA),]
df$RTr <- round(df$RT, digits = 3)
qqp(df$RT, "norm")
qqp(df$RT, "lnorm")
```

```{r}
interceptOnly <-gls(log(RT) ~ 1, data = df, 
                    method = "ML")
IDrandomInterceptOnlyt <-lmer(log(RT) ~ 1 + (1|ID), data = df)
StartlocationsrandomInterceptt <-lmer(log(RT)  ~ 1 + (1|ID) +  (1|TrialNumber), data = df)
```


```{r}
MeaningfulContext <-update(StartlocationsrandomInterceptt, .~. + ContextEffectf)
Presence <-update(MeaningfulContext, .~. + AgentPresencef)
TwofactorInteraction <-update(Presence, .~. + ContextEffectf*AgentPresencef)
summary(TwofactorInteraction)
Anova(TwofactorInteraction)
```
```{r}
Pairwise<- emmeans(TwofactorInteraction, pairwise ~ ContextEffectf*AgentPresencef)
Pairwise
plot(Pairwise[[2]], CIs = TRUE)
```

```{r}

CLD <- cld(Pairwise,
          alpha=0.05,
          Letters=letters,
          adjust="sidak")
ggplot(CLD,
       aes(x     = ContextEffectf,
           y     = emmean,
           group = AgentPresencef,
           colours = .group)) +

    geom_point(aes(shape=AgentPresencef, color=AgentPresencef), position=position_dodge(0.3)) +

    geom_errorbar(aes(color=AgentPresencef,
                      ymin  =  lower.CL,
                      ymax  =  upper.CL),
                      position=position_dodge(0.3),
                      width =  0.2,
                      size  =  0.7) +

    theme_bw() +
    theme(axis.title   = element_text(face = "bold"),
          axis.text    = element_text(face = "bold"),
          plot.caption = element_text(hjust = 0)) +

    ylab("Estimated marginal mean\ Response Time in Seconds") +
    xlab("Location location") +
    ggtitle ("Marginal Means",

             subtitle = "location * Presence") +

                 labs(caption  = paste0( 
                                   "Boxes indicate the EM mean. \n",
                                   "Error bars indicate the 95% ",
                                   "confidence interval of the EM mean. \n"),
                            hjust=0.5) 
```


```{r}
GHQ <- glmer(RT ~  ContextEffectf*AgentPresencef + (1|ID), data = HumanA,
    family=gaussian(link = "log"), nAGQ = 25)  
summary(GHQ)
Anova(GHQ)
anova(GHQ)
emmeans(GHQ, pairwise ~ ContextEffectf:AgentPresencef )
```
```{r}
HumanA$Agent_Category <- with(HumanA, ave(seq_along(ID), ID, FUN = function(x) sample(c(rep('Action', ceiling(length(x)*0.6)), rep('Standing', length(x) - ceiling(length(x)*0.6))))))
```

```{r }
library(dplyr)
TwoFactorTable <- HumanA %>% 
  group_by(ContextEffectf, AgentPresencef, Agent_Category)%>%
  summarise(AccuracyMean = mean(AbsolutError, na.rm = TRUE),
            n=n(),
            AccuracyStandardDev = sd(AbsolutError, na.rm = TRUE),
            RTMean = mean(RT, na.rm = TRUE),
            RTStandardDev = sd(RT, na.rm = TRUE))
library(tidyr)
TwoFactorTableUnite <- TwoFactorTable %>%
  unite("TwoFactor", ContextEffectf:Agent_Category, sep= " ", remove = F)
  
TwoFactorTableUnite <-  TwoFactorTableUnite %>%
  mutate( AccuracyStandardError=AccuracyStandardDev/sqrt(n)) %>%  
  mutate( AccuracyStandardIC=AccuracyStandardDev * qt((1-0.05)/2 + .5, n-1)) %>%
  mutate( RTStandardError=RTStandardDev/sqrt(n)) 

```



```{r}
ggplot(data=subset(TwoFactorTableUnite, !is.na(AgentPresencef)),
       aes(x     = ContextEffectf,
           y     = AccuracyMean,
           group = Agent_Category)) +

    geom_point(aes(shape=Agent_Category, linetype =Agent_Category), position=position_dodge(0.3)) +

    geom_errorbar(aes(linetype=Agent_Category,
                      ymin= AccuracyMean-AccuracyStandardError, 
                      ymax=AccuracyMean+AccuracyStandardError),
                      position=position_dodge(0.3),
                      width =  0.2,
                      size  =  0.7) +
  facet_wrap(~ AgentPresencef) +

    theme_bw() +
    theme(axis.title   = element_text(face = "bold"),
          axis.text    = element_text(face = "bold"),
          plot.caption = element_text(hjust = 0)) +

    ylab("Absolute angular error in degrees") +
    xlab("Location location") +
    ggtitle ("Accuracy performance",

             subtitle = "The effect of location  and presence") +

                 labs(caption  = paste0( 
                                   "Error bars indicate one Standard Error \n"),
                            hjust=0.5) 
```

# Loading Data 

```{r echo = FALSE, warning = FALSE}
HumanA_FixationsOne <- read.csv("/Volumes/TwoTeras/0_Experiment_1/Eye_Tracking/Pre_processed/Data_Sets/BehavioralData_Fixations_Wide.csv", sep =",")
head(HumanA_FixationsOne)
```
```{r}
HumanA_FixationsOne$ContextEffectf <-dplyr::recode(HumanA_FixationsOne$Context, 
                                      False = -0.5, True= 0.5,
                                      .default = NaN)
HumanA_FixationsOne$AgentPresence <-dplyr::recode(HumanA_FixationsOne$AvatarPresenceCategory,
                                             Omitted = -0.5, Present= 0.5,
                                             .default = NaN)
HumanA_FixationsOne$Agent_Action_level <-dplyr::recode(HumanA_FixationsOne$Agent_Action_level,
                                             Passive = -0.5, Active= 0.5,
                                             .default = NaN)
HumanA_FixationsOne$ContextEffectf <-factor(HumanA_FixationsOne$ContextEffectf,levels= c(-0.5, 0.5), 
                               labels=c('Residential', 'Public')) 
HumanA_FixationsOne$AgentPresencef <-factor(HumanA_FixationsOne$AgentPresence,
                                levels= c(-0.5, 0.5), 
                                labels=c('Omitted', 'Displayed'))
HumanA_FixationsOne$Agent_Action_levelf <-factor(HumanA_FixationsOne$Agent_Action_level,
                                levels= c(-0.5, 0.5), 
                                labels=c('Passive', 'Active'))
```

```{r}
library(dplyr)
TwoFactorTable_Fix_One <- HumanA_FixationsOne %>% 
  group_by(ContextEffectf, Agent_Action_levelf)%>%
  summarise(Dwelling_Time_Building_GazeMean = mean(Dwelling_Time_Building_Gaze, na.rm = TRUE),
            n=n(),
            Dwelling_Time_Building_GazeDev = sd(Dwelling_Time_Building_Gaze, na.rm = TRUE),
            Dwelling_Time_Agent_GazeMean = mean(Dwelling_Time_Agent_Gaze, na.rm = TRUE),
            Dwelling_Time_Agent_GazeDev = sd(Dwelling_Time_Agent_Gaze, na.rm = TRUE))
library(tidyr)
TwoFactorTable_Fix_OneUnite <- TwoFactorTable_Fix_One %>%
  unite("TwoFactor", ContextEffectf:Agent_Action_levelf, sep= " ", remove = F)
  
TwoFactorTable_Fix_OneUnite <-  TwoFactorTable_Fix_OneUnite %>%
  mutate( Dwelling_Time_Agent_Gaze_StandardError = Dwelling_Time_Agent_GazeDev/sqrt(n)) %>%  
  mutate( Dwelling_Time_Agent_GazeIC = Dwelling_Time_Agent_GazeDev * qt((1-0.05)/2 + .5, n-1)) %>%
  mutate( Dwelling_Time_Building_Gaze_StandardError = Dwelling_Time_Building_GazeDev/sqrt(n)) 
```

```{r}
Acc <- ggplot(data = subset(TwoFactorTable_Fix_OneUnite, !is.na(Agent_Action_levelf)),
              aes(x = ContextEffectf,
                  y = Dwelling_Time_Building_GazeMean,
                  group = Agent_Action_levelf))

Acc + geom_point(aes(shape = Agent_Action_levelf, linetype = Agent_Action_levelf), position = position_dodge(0.3)) +
  geom_errorbar(aes(linetype = Agent_Action_levelf, ymin = Dwelling_Time_Building_GazeMean - Dwelling_Time_Building_Gaze_StandardError, 
                    ymax = Dwelling_Time_Building_GazeMean + Dwelling_Time_Building_Gaze_StandardError),
                position = position_dodge(0.3),
                width = 0.2,
                size = 0.7) +
  theme_bw() +
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold"),
        legend.position="top",
        legend.background = element_rect(fill="gray88",
                                  size=0.5, linetype="solid", 
                                  colour ="gray88"),
        plot.caption = element_text(hjust = 0))  +
  ylab("Dwelling Time of target buildings in Seconds") +
  xlab("Location") +
  ggtitle("Dwelling Time of target buildings",
          subtitle = "The effects of location and agent category on Dwelling Time Building") +
  labs(caption = paste0("Error bars indicate one Standard Error \n"))
```

```{r warning = FALSE }
df_Fix_One = HumanA_FixationsOne[complete.cases(HumanA_FixationsOne),]
df_Fix_One$AbsolutErrorR <- round(df_Fix_One$AbsolutError, digits = 3)
qqp(df_Fix_One$AbsolutErrorR, "norm")
qqp(df_Fix_One$AbsolutErrorR, "lnorm")

# Set up contrast to sum zero A.K.A compare each level equally
contrasts(df_Fix_One$ContextEffectf) <- "contr.sum"
contrasts(df_Fix_One$AgentPresencef) <- "contr.sum"
contrasts(df_Fix_One$Agent_Action_levelf) <- "contr.sum"
```


```{r}
interceptOnly_Agent<-gls(AbsolutErrorR ~ 1, data = df_Fix_One, 
                    method = "ML")
IDrandomInterceptOnly_Agent <-lmer(AbsolutErrorR ~ 1 + (1|SubjectID), data = df_Fix_One)
TrialIDrandomIntercept_Agent <-lmer(AbsolutErrorR ~ 1 + (1|StartPointID) + (1|SubjectID), data = df_Fix_One)
```

```{r}
TwofactorInteraction_Agent <-update(TrialIDrandomIntercept_Agent, .~. +  Dwelling_Time_Building_Gaze+ Dwelling_Time_Agent_Gaze)
summary(TwofactorInteraction_Agent)
Anova(TwofactorInteraction_Agent)
```

```{r}
tab_model(TwofactorInteraction_Agent)
```

```{r}
b <- ggplot(df_Fix_One, aes(x = AbsolutErrorR, y = Dwelling_Time_Building_Gaze))
# Scatter plot with regression line
b + geom_point()+
  geom_smooth(method = "lm") 
     
# Add a loess smoothed fit curve
b + geom_point()+
  geom_smooth(method = "loess") 
```
```{r}
plot_model(TwofactorInteraction_Agent, type="re")
plot_model(TwofactorInteraction_Agent, type="est")
plot_model(TwofactorInteraction_Agent, type="pred")
plot_model(TwofactorInteraction_Agent, type="int", mdrt.values = "quart")
```


```{r}
plot_model(TwofactorInteraction_Agent, show.values = TRUE, value.offset = .3, colors="bw",  vline.color = "red")
```
```{r}
Complete_model <-update(TrialIDrandomIntercept_Agent, .~. +  Dwelling_Time_Building_Gaze + Dwelling_Time_Agent_Gaze + ContextEffectf*Agent_Action_levelf  + AgentPresencef )
summary(Complete_model)
Anova(Complete_model)
```
```{r}
plot_model(Complete_model, show.values = TRUE, value.offset = .3, colors="bw",  vline.color = "red")
tab_model(Complete_model, pred.labels=c("Intercept", "Dwealling time on task Building",  "Dwealling time on agent","Location context (Public vs. Residential)", "Agent Presence in Task Stimuli"))
```
```{r}
plot_model(Complete_model, type="re")
plot_model(Complete_model, type="est")
plot_model(Complete_model, type="pred")
plot_model(Complete_model, type="int", mdrt.values = "quart")
```


